Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-24 paper_jasa.tex
small latex error

\begin{dfn}\label{dfn:error}
The \textbf{Type I error} is the probability of \red{rejecting $H_0$ when it is true, the probability for that is $P(X \ge x_{1-\alpha})$, which is controlled by $\alpha$. Note that due to the discrete nature of $X$ we can not always control exactly for $\alpha$. }
% identifying the observed data plot, when $H_0$ is true, which is $1/m$, and is thus controlled by the number of null plots. 
\textbf{Type II error} is the probability of failing to identify the observed data plot, when $H_0$ is not true, \red{i.e. $P( X \le x_{1-\alpha$}), where $x_{1 - \alpha}$ is the (approximate) $1-\alpha$ quantile of  $B_{K, 1/m}$, the distribution of $X$ under the null hypothesis.}
\red{Under the alternative hypothesis, we have to account for different visual abilities of  individuals: let $X_i$ be a binary random variable with $X_i = 1$, if individual $i$ identifies the data plot from the lineup, and $X_i = 0$ otherwise.  Then $X_i \sim B_{1, p_i}$ and $X = \sum_i X_i$ has  a Poisson-Binomial distribution.}
\end{dfn}

>>>>

\begin{dfn}\label{dfn:error}
The \textbf{Type I error} is the probability of \red{rejecting $H_0$ when it is true, the probability for that is $P(X \ge x_{1-\alpha})$, which is controlled by $\alpha$. Note that due to the discrete nature of $X$ we can not always control exactly for $\alpha$. }
% identifying the observed data plot, when $H_0$ is true, which is $1/m$, and is thus controlled by the number of null plots. 
\textbf{Type II error} is the probability of failing to identify the observed data plot, when $H_0$ is not true, \red{i.e. $P( X \le x_{1-\alpha})$, where $x_{1 - \alpha}$ is the (approximate) $1-\alpha$ quantile of  $B_{K, 1/m}$, the distribution of $X$ under the null hypothesis.}
\red{Under the alternative hypothesis, we have to account for different visual abilities of  individuals: let $X_i$ be a binary random variable with $X_i = 1$, if individual $i$ identifies the data plot from the lineup, and $X_i = 0$ otherwise.  Then $X_i \sim B_{1, p_i}$ and $X = \sum_i X_i$ has  a Poisson-Binomial distribution.}
\end{dfn}
